Frequency of dwarf and massive galaxy pairs in the IllustrisTNG cosmological simulation

### 2023-02-16 paper/pears.tex
slight updates to scaled plot captions
minor changes to scaled captions reflecting z>4 change
added text on pair frac plot

% Packages
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{tikz}
\usepackage{xcolor}

@@

\begin{abstract}
  \todo{REMEMBER TO USE 100-1000 REALS IN PLOTS}
  \todo{Include ticks on top and right axis as well}
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sample selection}\label{sec:methods}
% methods plots
  \begin{figure*}[htp]
    \centering
    \includegraphics[width=\textwidth]{counts_1000.png}
    \caption{(Top) Median number of dwarf (left) and massive (right) primaries and pairs per abundance matching realization as a function of redshift.
    Shaded regions show the $1^{\rm st}$ and 99$^{\rm th}$ percentile spread of the medians of all realizations. 
    There are approximately 8 times as many dwarf primaries as massive primaries. 
    % dwarf galaxies
    The dwarf primary count (green solid line in top left panel) is at a minimum at $z=4$, rises to a maximum of $\sim15000$ halos per realization by $z=1$, then decreases by $\sim16\%$ to 12000 halos at $z=0$. The dwarf pair count (green dashed line), on the other hand, peaks at $z\sim2$ with 3000 pairs, and decreases to a minimum of about 1000 pairs at $z=0$.
    % Massive galaxies (right)
    The massive primary count (pink solid line in top right panel) behaves similarly to the dwarf primary count, with a minimum count at $z=4$ which rises to a maximum of $\sim2000$ halos per realization at $z\sim1$, then decreases slightly by $\sim5\%$ to $\sim$1800 halos by $z=0$. 
    Unlike dwarf pairs whose pair count peaks at $z=2$, pair count for massive galaxies (pink dashed line) follows similar behavior to the total massive primary count, with a minimum at $z=4$, and increasing to $z=\sim 1$ before leveling off. At very low redshift, the pair count and primary count have opposite behavior, with the pair count \textit{increasing} at very low redshifts of $z=0-0.25$ and \textit{peaking} at $z=0$.
    (Bottom) Fraction of pairs per primary as a function of redshift (i.e., the ratio between dotted line and solid line in each column). Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$. The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.}
    \label{fig:counts}
  \end{figure*}

@@

%%%%%%%%%%%
%%%%%%%%%%%
\subsection{Abundance matching prescription}\label{sec:methods-am}
% Why do we need stellar masses?
One of the goals of this study is to determine the impact of baryonic physics on the occurance rate and typical separations of galaxy \kc{subhalo?} pairs in cosmological simulations. 
However, selecting halo pairs by stellar mass ratio using the stellar masses provided by the simulations is not possible in the dark matter only runs. 
Thus, in order ensure the dark matter only and full hydrodynamic samples are self-consistent, we need to associate each of the selected subhalos with a realistic stellar mass.

@@

We create 1000 stellar mass realizations from the SMHM relationship, thus accounting for the systematic uncerntainy in subhalo stellar masses. Each realization is treated as an independent sample, such that computed properties (pair frequency, separations, etc) are given as the median each realization. We report the mean of all realizations and error bars indicate the 1$\sigma$ dispersion across the realizations.
%%%%%%%%%%%
%%%%%%%%%%%
\subsection{Selection criteria}\label{sec:methods-crit}
In this section, we outline the selection criteria used to select dwarf and massive subhalo pairs. 
The same selection criteria is utilized for all four simulations (\illd, \illh, \tngd, and \tngh)
In short, blah. 
Detailed steps are as follows.

@@

\subsection{Pair fraction}\label{sec:results-frac}
%% text on pair fraction plot
\kc{WIP} Thus, the rate of dwarf pairs and massive pairs \textit{per primary} will evolve distinctly in the dwarf and massive pair case.

%% pair fraction plot
\label{sec:results}
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{pairratio_1000.png}
  \caption{
    % Top plots ~
    (Top) Median fraction of dwarf or massive primaries with a major or minor companion by stellar mass. 
    Shaded regions show the $1$-$99$ percentile range of the median pair fractions of each realization. 
      % massive pairs
    The fraction of massive primaries (pink) with a major (left) or minor (right) companion remains approximately constant for $z>1$, with an average pair fraction of 0.16-0.17 and 0.14-0.15 respectively. Between $z=0.25$ and $z=0$, the massive major pair fraction increases sharply from 0.165 to 0.207, a 25\% increase, while the minor pair fraction increases from 0.127 to 0.152, a 20\% increase.
      % dwarf pairs
    Dwarf pairs (green), on the other hand, have pair fractions that are approximately constant from $z=3-4$, but the fraction of major(minor) pairs declines monotonically from 0.126(0.111) at x=3 to just 0.041(0.034) at x=0, a 67(70)\% decrease. 
    % Bottom plots ~
  (Bottom) The median subtracted difference between the massive pair fraction and the dwarf pair fraction, with the shaded $1$-$99$ percentile range of the difference of each realization. The difference between the massive pair fraction and dwarf pair fraction increases with decreasing redshift, peaking at $z=0$ with a difference of 0.166 for major pairs and 0.111 for minor pairs. This shows that the redshift evolution of the pair fractions of massive pairs and dwarf pairs proceed differently, particularly in the low redshift regime.}
  \label{fig:pairratio}
\end{figure*}

@@

@@

\todo{quick final conclusions on separations}

\kc{here maybe include a table? what are some values?  z=0,1,2,3,4 and pair frac, sep, vel. ?}

%% separation plots
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{separation_1000.png}
  \caption{(Top) Median physical separation (in kpc) of dwarf pairs (left, green) and massive pairs (right, pink) as a function of redshift. 
  Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
  Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
  In general, as the redshift decreases from $z=4$ to $z=0$, the average physical separation of a pair increases for both dwarf and massive pairs. 
  % Dwarf pairs
  The redshift evolution of the dwarf pairs closely resembles a power law distribution across the whole redshift range from $z=0-4$.
  At $z=4$, the typical separation between major (minor) dwarf pairs is $42(38)\,\kpc$, and peaks at $z=0$ with a median separation of $128(109)\,\kpc$.
  % Massive Pairs
  The separation between massive pairs, on the other hand, increases approximately linearly from $z=4$, where the median separations of major (minor) pairs is $81(71)\,\kpc$, to $z=1$, where median separations are $171(124)\,\kpc$. The median separation rises more steeply from z=1 to z=0, peaking around $z=\sim0$ at $288\,\kpc$ and $205\,\kpc$ for major and minor massive pairs respectively.
  % Difference plots
  (Bottom) The median subtracted separation difference between major and minor pairs, and 1-99\% shaded region.
  Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs. 
    }
  \label{fig:sep}
\end{figure*}

@@

@@

%% velocity plots 
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{velocity_1000.png}
  \caption{
    (Top) Median relative velocity (in \kms) between the primary and secondary halos of: dwarf pairs (left, green), and massive pairs (right, pink) as a function of redshift. 
    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
    The overall behavior of the redshift evolution is nearly identical for dwarf and massive pairs.
    As the redshift decreases from $z=4$ to $z=0$, the average relative velocity of a pair decreases as well for both dwarf and massive pairs.
    % brief describe
    The median relative velocity of a dwarf pair (major or minor) is $70\,\kms$ at $z=0$ and $133\,\kms$ at $z=4$, and of a massive pair is $170\,\kms$ at $z=0$ and $260\,\kms$ at $z=4$ ($295\,\kms$ for a minor pair). 
    % Difference plot
    (Bottom) The median subtracted relative velocity difference between major and minor pairs, and 1-99\% shaded region.
    The is little difference between major and minor dwarf pairs (bottom left), with minor pairs having a relative velocity of $0-5\,\kms$ higher than major pairs. 
    Major and minor massive pairs also have very little median velocity difference at low redshift (bottom right), with minor pairs having a relative velocity between $1-20\,\kms$ faster than major pairs.
    }
  \label{fig:vel}
\end{figure*}

@@

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{scaledsep.png}
  \caption{Median scaled separation (separation of a pair divided by the virial radius of its group) as a function of redshift. Dwarf pairs (major (solid) and minor (dashed)) tend to have smaller scaled separations at lower redshifts, leveling out between $z=0-1$. In particular, the secondaries of dwarf major pairs at $z>2$ tend to live more than one virial radius away from the primary. Massive major pairs at low redshift tend to have smaller scaled separations  at $z<\sim2$, but vary significantly at higher redshifts. 
  Minor pairs (right), both dwarf and massive, tend to have smaller separations, tending to live closer than one virial radius between the primary and secondary. Massive minor pairs tend to have smaller scaled separations compared to dwarf pairs at all redshifts.
  \todo{replace with 1000 reals fig, finish caption, add 0 horizon line}
    }
  \label{fig:sep-scaled}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{scaledsep_distribution.png}
  \caption{\todo{finish caption, 1000 reals, change median color, add z=4}}
  \label{fig:sep-scaled-dist}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{scaledvel.png}
  \caption{Median scaled velocity (relative velocity of a pair divided by the virial velocity), defined as the circular velocity at the virial radius of the group as a function of redshift. 
  Major pairs are on the left (solid lines), minor pairs are on the right in dashed lines.
  All sets of pairs show an increase in scaled velocity at lower redshifts.
  \todo{finish caption, replace with 1000 reals, add 0 horizon line}
  }
  \label{fig:vel-scaled}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{scaledvel_distribution.png}
  \caption{\todo{finish caption, 1000 reals, change median color, add z=4}}
  \label{fig:vel-scaled-dist}
\end{figure*}

\kc{add discussion subsection titles}
\subsection{Dwarf and massive pair kinematic differences}
\subsection{Comparison to literature}
\subsection{Implications for observations}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Conclusions}
\label{sec:summary}

>>>>

% Packages
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{soul}

@@

\begin{abstract}
  \todo{REMEMBER TO USE 100-1000 REALS IN PLOTS}

  \todo{Include ticks on top and right axis as well}

  \todo{Remove all instances of "we find" to "we compute" or "we calculate"}
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sample selection}\label{sec:methods}
% methods plots
  \begin{figure*}[htp]
    \centering
    \includegraphics[width=\textwidth]{counts_1000.png}
    \caption{(Top) \kc{correct wording: Median number of dwarf (left) and massive (right) primaries and pairs per abundance matching realization as a function of redshift.} 
    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations, as described in Sec.~\ref{sec:methods-err}.
    There are approximately 8 times as many dwarf primaries as massive primaries. 
    % dwarf galaxies
    The dwarf primary count (green solid line in top left panel) is at a minimum at $z=4$, rises to a maximum of $\sim15000$ halos per realization by $z=1$, then decreases by $\sim16\%$ to 12000 halos at $z=0$. The dwarf pair count (green dashed line), on the other hand, peaks at $z\sim2$ with 3000 pairs, and decreases to a minimum of about 1000 pairs at $z=0$.
    % Massive galaxies (right)
    The massive primary count (pink solid line in top right panel) behaves similarly to the dwarf primary count, with a minimum count at $z=4$ which rises to a maximum of $\sim2000$ halos per realization at $z\sim1$, then decreases slightly by $\sim5\%$ to $\sim$1800 halos by $z=0$. 
    Unlike dwarf pairs whose pair count peaks at $z=2$, pair count for massive galaxies (pink dashed line) follows similar behavior to the total massive primary count, with a minimum at $z=4$, and increasing to $z=\sim 1$ before leveling off. At very low redshift, the pair count and primary count have opposite behavior, with the pair count \textit{increasing} at very low redshifts of $z=0-0.25$ and \textit{peaking} at $z=0$.
    (Bottom) Fraction of pairs per primary as a function of redshift (i.e., the ratio between dotted line and solid line in each column). Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$. The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.}
    \label{fig:counts}
  \end{figure*}

@@

%%%%%%%%%%%
%%%%%%%%%%%
\subsection{Abundance matching prescription}\label{sec:methods-am}
% Why do we need stellar masses?
One of the goals of this study is to determine the impact of baryonic physics on the occurrence rate and typical separations of galaxy \kc{subhalo?} pairs in cosmological simulations. 
However, selecting halo pairs by stellar mass ratio using the stellar masses provided by the simulations is not possible in the dark matter only runs. 
Thus, in order ensure the dark matter only and full hydrodynamic samples are self-consistent, we need to associate each of the selected subhalos with a realistic stellar mass.

@@

We create 1000 stellar mass realizations from the SMHM relationship, thus accounting for the systematic uncerntainy in subhalo stellar masses. Each realization is treated as an independent sample, such that computed properties (pair frequency, separations, etc) are given as the median each realization. We report the mean of all realizations and error bars indicate the 1$\sigma$ dispersion across the realizations.

\subsubsection{Error calculations}\label{sec:methods-err}

%%%%%%%%%%%
%%%%%%%%%%%
\subsection{Selection criteria}\label{sec:methods-crit}
In this section, we outline the selection criteria used to select dwarf and massive subhalo pairs. 
The same selection criteria is utilized for all four simulations (\illd, \illh, \tngd, and \tngh)
In short, blah. 
Detailed steps are as follows.

@@

\subsection{Pair fraction}\label{sec:results-frac}
%% text on pair fraction plot
The pair fraction is defined here as the fraction of identified dwarf or massive primaries with a major or minor companion (see Sec.~\ref{sec:methods-crit} for more info on selection criteria for major and minor pairs). 
Fig.~\ref{fig:pairratio} shows the calculated pair fractions for massive and dwarf pairs (including both major and minor pairs separately) as a function of time for $z=0-4$.

    % differences between major and minor pairs? 
The minor pair fraction of both massive and dwarf pairs tends to be smaller than that of major pairs of the same mass range at all redshifts. This is likely because of the lower stellar mass ratio limit we put on our pairs. \kc{take away -- why? what does the difference between major and minor mean? check g's 2018 paper for discussion}

    % differences between massive and dwarf pairs? 
Additionally, dwarf and massive pair fractions evolve distinctly over this redshift range -- the mass pair fraction is roughly flat/constant, while the dwarf pair fraction declines from $z=\sim 2-3$ to a minimum at $z=0$.  
The subtracted difference between the pair fractions of massive and dwarf pairs (respectively) is low and flat at high z (z=$2-4$), but increases up to $\sim0.12-0.18$ by $z=0$. 
Thus, our expectations for massive and dwarf pair counts should evolve very differently at low redshift, despite being roughly equivalent at higher z. 
The implications of the difference in the evolution of pair fractions for dwarf and massive pairs across time is discussed in detail in Sec.~\ref{sec:discussion}.

%% pair fraction plot
\label{sec:results}
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{pairratio_1000.png}
  \caption{
    % Top plots ~
    (Top) Median fraction of dwarf or massive primaries with a major or minor companion by stellar mass. 
    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
      % massive pairs
    The fraction of massive primaries (pink) with a major (left) or minor (right) companion remains approximately constant for $z>1$, with an average pair fraction of 0.16-0.17 and 0.14-0.15 respectively. Between $z=0.25$ and $z=0$, the massive major pair fraction increases sharply from 0.165 to 0.207, a 25\% increase, while the minor pair fraction increases from 0.127 to 0.152, a 20\% increase.
      % dwarf pairs
    Dwarf pairs (green), on the other hand, have pair fractions that are approximately constant from $z=3-4$, but the fraction of major(minor) pairs declines monotonically from 0.126(0.111) at x=3 to just 0.041(0.034) at x=0, a 67(70)\% decrease. 
    % Bottom plots ~
  (Bottom) The median subtracted difference between the massive pair fraction and the dwarf pair fraction, with the shaded $1$-$99$ percentile range of the difference of each realization. The difference between the massive pair fraction and dwarf pair fraction increases with decreasing redshift, peaking at $z=0$ with a difference of 0.166 for major pairs and 0.111 for minor pairs. This shows that the redshift evolution of the pair fractions of massive pairs and dwarf pairs proceed differently, particularly in the low redshift regime.\todo{remove "difference" label, explain in capt. what "diff" means}}
  \label{fig:pairratio}
\end{figure*}

@@

\kc{key takeaways}
\kc{what do I want to say about this figure? This makes sense because as the universe evolves, structures become bigger and you start increasing the material accreted in the outer regions of the halo, so it not surprising to see an increasing median separation towards lower redshifts. }
\kc{halo mass sets the scale of the typical separations of objects.}
\kc{We leave the discussion on the implications of the evolution of median separations on pair selection criteria for sec.~\ref{sec:discussion}}
\kc{This begs the question: what does this mean for selection criteria for pairs at different mass scales and at different redshifts?}
\kc{The general trend for pairs of all mass types is for higher seps at lower z. Also, minor pairs tend to live at closer separations than their major counterparts. This is likely because close major pairs are more likely to merge more quickly than minor pairs, so you aren't left with many close major pairs since they have merged at higher z.}

@@

\kc{table? z=0,1,2,3,4 and pair frac, sep, vel. ?}

%% separation plots
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{separation_1000.png}
  \caption{(Top) Median physical separation (in kpc) of dwarf pairs (left, green) and massive pairs (right, pink) as a function of redshift. 
  Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
  Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
  In general, as the redshift decreases from $z=4$ to $z=0$, the average physical separation of a pair increases for both dwarf and massive pairs. 
  % Dwarf pairs
  The redshift evolution of the dwarf pairs \remove{\st{closely resembles a power law distribution}} across the whole redshift range from $z=0-4$.
  At $z=4$, the typical separation between major (minor) dwarf pairs is $42(38)\,\kpc$, and peaks at $z=0$ with a median separation of $128(109)\,\kpc$.
  % Massive Pairs
  The separation between massive pairs, on the other hand, increases approximately linearly from $z=4$, where the median separations of major (minor) pairs is $81(71)\,\kpc$, to $z=1$, where median separations are $171(124)\,\kpc$. The median separation rises more steeply from z=1 to z=0, peaking around $z=\sim0$ at $288\,\kpc$ and $205\,\kpc$ for major and minor massive pairs respectively.
  % Difference plots
  (Bottom) The median subtracted separation difference between major and minor pairs, and 1-99\% shaded region.
  Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs. \todo{remove "difference" legend, explain in capt. what "Maj-Min" means}
    }
  \label{fig:sep}
\end{figure*}

@@

\kc{key takeaways}

@@

%% velocity plots 
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{velocity_1000.png}
  \caption{
    (Top) Median relative velocity (in \kms) between the primary and secondary halos of: dwarf pairs (left, green), and massive pairs (right, pink) as a function of redshift. 
    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
    The overall behavior of the redshift evolution is nearly identical for dwarf and massive pairs.
    As the redshift decreases from $z=4$ to $z=0$, the average relative velocity of a pair decreases as well for both dwarf and massive pairs.
    % brief describe
    The median relative velocity of a dwarf pair (major or minor) is $70\,\kms$ at $z=0$ and $133\,\kms$ at $z=4$, and of a massive pair is $170\,\kms$ at $z=0$ and $260\,\kms$ at $z=4$ ($295\,\kms$ for a minor pair). 
    % Difference plot
    (Bottom) The median subtracted relative velocity difference between major and minor pairs, and 1-99\% shaded region.
    The is little difference between major and minor dwarf pairs (bottom left), with minor pairs having a relative velocity of $0-5\,\kms$ higher than major pairs. 
    Major and minor massive pairs also have very little median velocity difference at low redshift (bottom right), with minor pairs having a relative velocity between $1-20\,\kms$ faster than major pairs.
    \todo{remove "difference" legend, explain in capt. what "Maj-Min" means}
    }
  \label{fig:vel}
\end{figure*}

@@

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{scaledsep_1000.png}
  \caption{Median scaled separation (separation of a pair divided by the virial radius of its group) as a function of redshift. Dwarf pairs (major (solid) and minor (dashed)) tend to have smaller scaled separations at lower redshifts, leveling out between $z=0-1$. In particular, the secondaries of dwarf major pairs at $z>2$ tend to live more than one virial radius away from the primary. Massive major pairs at low redshift tend to have smaller scaled separations  at $z<\sim2$, but vary significantly at higher redshifts. 
  Minor pairs (right), both dwarf and massive, tend to have smaller separations, tending to live closer than one virial radius between the primary and secondary. Massive minor pairs tend to have smaller scaled separations compared to dwarf pairs at all redshifts.
  \todo{finish caption} \todo{remove "difference" legend, explain in capt. what "Ma-Dw" means}
    }
  \label{fig:sep-scaled}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{scaledsep_distribution_1000.png}
  \caption{\todo{finish caption}}
  \label{fig:sep-scaled-dist}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{scaledvel_1000.png}
  \caption{Median scaled velocity (relative velocity of a pair divided by the virial velocity), defined as the circular velocity at the virial radius of the group as a function of redshift. 
  Major pairs are on the left (solid lines), minor pairs are on the right in dashed lines.
  All sets of pairs show an increase in scaled velocity at lower redshifts.
  \todo{finish caption} \todo{remove "difference" legend, explain in capt. what "Maj-Min" means}
  }
  \label{fig:vel-scaled}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{scaledvel_distribution_1000.png}
  \caption{\todo{finish caption}}
  \label{fig:vel-scaled-dist}
\end{figure*}

\kc{add discussion subsection titles}
\subsection{Dwarf and massive pair kinematic differences}
\subsection{Comparison to literature}
\subsection{Implications for observations}
\subsection{Implications for observational pair selection criteria}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Conclusions}
\label{sec:summary}
Findings:
\begin{itemize}
    \item Pair fraction for dwarfs and massives does not proceed identically throughout cosmic time. Opposite behavior at low z. 
    \item Median pair separations increase and relative velocities decrease from high to low redshift. 
    \item Minor dwarf and massive pairs exhibit 
\end{itemize}
